Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-10 article/article.tex
new car
mozes

Temporal dimensionality reduction. As described in the introduction, the peak of the BOLD response is approximately 5 seconds after a stimulus is presented. This means that the first scans after a stimulus may not represent activity related to this stimulus and should not be used for classification. To examine which scans provide maximal class information, we plotted the average BOLD activity per scan for all trials of all subjects, given a trial type and ROI. As can be seen in Figure, scans 10 to 20 provide maximal information for the first stimulus, while scans 23 to 33 provide maximal information for the second stimulus. The other scans were excluded. As a comparison,

\subsection{Classifiers}

>>>>

Temporal dimensionality reduction. As described in the introduction, the peak of the BOLD response is approximately 5 seconds after a stimulus is presented. This means that the first scans after a stimulus may not represent activity related to this stimulus and should not be used for classification. To examine which scans provide maximal class information, we plotted the average BOLD activity per scan for all trials of all subjects, given a trial type and ROI. As can be seen in Figure~\ref{fig:boldroi}, scans 10 to 20 provide maximal information for the first stimulus, while scans 23 to 33 provide maximal information for the second stimulus. The other scans were excluded.      
\begin{figure}
	\centering
	\includegraphics[width=90mm]{figures/scan_hemodynamic_BOLD_roi}
  	\caption{Haemodynamic BOLD response for ROI "CALC". Average Bold activity for all subjects is plotted against the scan number. The coloured regions depict an interval of 1 standard deviation.}
  	\label{fig:boldroi}
\end{figure}
\subsection{Classifiers}
